Financialisation of commodities: co-movement behind-the-scenes

### 2022-06-30 docs/paper.Rmd

```{r, include=latex}
knitr::asis_output('\\newgeometry{a4paper,left=1in,right=1in,top=1in,bottom=1in,nohead}')
knitr::asis_output('\\savegeometry{tables}')
knitr::asis_output('\\restoregeometry')
```

>>>>

```{r, include=latex}
knitr::asis_output('\\newgeometry{left=1in,right=1in,top=1in,bottom=1in,nohead}')
knitr::asis_output('\\savegeometry{tables}')
knitr::asis_output('\\restoregeometry')
```
